Verification of Stencil Computations with Spatial Specifications

### 2016-11-12 paper.tex
representing consistency

\newcommand{\trule}[1]{{\footnotesize{#1}}}
%\include{results}

@@

@@

%\newcommand{\cons}[3]{\mathbf{C}_{#3}(#1, #2)}
\newcommand{\cons}[3]{#2 \;\, \textbf{consistent} \,\, #1}
\begin{align*}
\dfrac{\forall u \in C, \exists v \in S .  \, u \preceq v}
      {\cons{\mathsf{up}(S)}{C}{n}}
\qquad
\dfrac{\forall v \in S, \exists u \in C . \, u \preceq v}
      {\cons{\mathsf{low}(S)}{C}{n}} \\[0.75em]
\dfrac{\cons{\mathsf{down}(S)}{C}{n} \qquad \cons{\mathsf{up}(S)}{C}{n}}
  {\cons{\mathsf{exact}(S)}{C}{n}} \\[0.75em]
\dfrac{\cons{\mathsf{down}(S_1)}{C}{n} \qquad \cons{\mathsf{up}(S_2)}{C}{n}}
  {\cons{\mathsf{both}(S_1, S_2)}{C}{n}}
\end{align*}

>>>>

\newcommand{\trule}[1]{{\footnotesize{(\text{#1})}}}
%\include{results}

@@

%\newcommand{\cons}[3]{\mathbf{C}_{#3}(#1, #2)}
\newcommand{\cons}[3]{#2 \;\, \textbf{cons} \,\, #1}
\newcommand{\consA}[3]{#2 \;\, \textbf{cons}_M \,\, #1}

@@

\begin{definition}
Consistency is defined in terms of the binary predicate
$\textbf{cons}$ in Figure~\ref{fig:consistency}.
Consistency relates models of source code and models 
of specifications (which are bounded), thus
 $\textbf{cons} \subseteq \mathcal{P}(\domainVal{}^n)
\times \textsf{Approx}(\mathcal{P}(\domainVal{}^n))$. 
We denote sets of indexing schemes $\mathcal{P}(\domainVal{}^n)$
that come from a specification model by $S$ and from source code model
by $C$.

Rules (\emph{up}) and (\emph{low}) are the core rules relating models of
specifications and models of code. The (up) rule 
considers the case where the specification is
an \term{atMost} upper-bound approximation.
An upper bound specification means that for every scheme in the code
model, modelling a source-level index, $\forall u \in C$ there exists
a generalising scheme in the spec model $\exists v \in S$, \ie{}, $u
\preceq v$. That is, every source-level index scheme is generalised by the specification.
The (down) rule provides the case of 
\term{atLeast} lower-bound specifications. Consistency is dual to the above: 
for every scheme in the specification model $\forall v \in S$ there
exists a scheme in the code model $\exists u \in C$ such that $u
\preceq v$. That is, every specification scheme is generalised by some source
index scheme.

The (\emph{up}) and (\emph{down}) rules are combined for an \textsf{exact}
specification (\textit{exact}) such that a specification's model
provides both a consistent lower and consistent upper bound on
for the source code. Thus, for every scheme in the code model there
is a scheme in the spec model that generalises it, and for every
scheme in the spec model there is a scheme in the source model that
specialises it.  The (\textit{both}) rule is similar, decomposing
a specification which has both a lower and upper bound into
consistency of these bounds.

Rules $(1)$ and $(*)$ extend the $\textbf{cons}$
predicate to $\textbf{cons}_M \subseteq
\textsf{Mult}(\mathcal{P}(\domainVal{}^n)) 
\times \textsf{Mult}(\textsf{Approx}(\mathcal{P}(\domainVal{}^n)))$
which inludes multiplicity information. Both rules 
state that consistent models remain consistent if they
have the same multiplicity. Relatedly, rule $(1 < *)$ ensures
that absence of a \texttt{readOnce} modifier in the specification
does not prohibit a set of unique stencil accesses in the
code from being consistent.
\end{definition}

\begin{figure}[t]
\begin{align*}
\begin{array}{c}
%%
\trule{up}\dfrac{\forall u \in C \, \exists v \in S .  \, u \preceq v}
      {\cons{\textsf{upper}(S)}{C}{n}}
\qquad
\trule{low}\dfrac{\forall v \in S \, \exists u \in C . \, u \preceq v}
      {\cons{\textsf{lower}(S)}{C}{n}} \\[1.5em]
%%
\trule{exact}\dfrac{\cons{\textsf{lower}(S)}{C}{n} \qquad \cons{\textsf{upper}(S)}{C}{n}}
  {\cons{\textsf{exact}(S)}{C}{n}} \\[1.5em]
%%
\trule{both}\dfrac{\cons{\textsf{lower}(S_1)}{C}{n} \qquad \cons{\textsf{upper}(S_2)}{C}{n}}
  {\cons{\textsf{both}(S_1, S_2)}{C}{n}}\\[1.5em]
%%
\trule{$1$}
\dfrac{\cons{S}{C}{n}}{\consA{\textsf{once}(S)}{\textsf{once}(C)}{n}}
\;\;
\trule{$*$}
\dfrac{\cons{S}{C}{n}}{\consA{\textsf{mult}(S)}{\textsf{mult}(C)}{n}}
  \\[1.5em]
\trule{$1 < *$}
\dfrac{\cons{S}{C}{n}}{\consA{\textsf{mult}(S)}{\textsf{once}(C)}{n}}
\end{array}
\end{align*}
\caption{Consistency between models of code and specification}
\label{fig:consistency}
\vspace{-0.9em}
\end{figure}
